Expected Dependency Pair Match:\\ Predicting translation quality with expected syntactic structure

### 2009-07-29 mtjournal.tex
added justification subclause to sentence about modification to head-finding rules

In this work, we use a state-of-the-art PCFG (the first stage of
\inlinecite{charniak-johnson:2005:ACL}) and context-free head-finding
rules \cite{magerman95headfinding} to generate a 50-best list of
dependency trees for each hypothesis and reference translation.  We
use the parser's default (English-language) Wall Street Journal
training parameters.  Head-finding uses the Charniak parser's rules,
with three modifications: prepositional and complementizer phrases
choose nominal and verbal heads respectively (rather than functional
heads) and auxiliary verbs are modifiers of main verbs (rather than
the converse).

>>>>

In this work, we use a state-of-the-art PCFG (the first stage of
\inlinecite{charniak-johnson:2005:ACL}) and context-free head-finding
rules \cite{magerman95headfinding} to generate a 50-best list of
dependency trees for each hypothesis and reference translation.  We
use the parser's default (English-language) Wall Street Journal
training parameters.  Head-finding uses the Charniak parser's rules,
with three modifications to make the semantic (rather than syntactic)
relations more dominant in the dependency tree: prepositional and
complementizer phrases choose nominal and verbal heads respectively
(rather than functional heads) and auxiliary verbs are modifiers of
main verbs (rather than the converse).
